### 2015-09-02 Projects/DelCo_2012/Report/DelCo_2012.tex
update Delco 2012

\headerC{
{
\flushright{
Daniel Madrzykowski \\
Keith M. Stakes \\
Craig G. Weinschenk \\

@@

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/Spray_Distribution}
% 	\caption{Collector Bins and Plastic Sheathing in Experimental Structures}
% 	\label{fig:Spray_Density_Set_Up}
% \end{figure}

@@

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/Spray_Hall}
% 	\caption{Hallway Nozzle Location for Fire Suppression Tests}
% 	\label{fig:Hallway_Nozzle_Location_Fire_Suppression_Tests}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/Spray_Room}
% 	\caption{Room Nozzle Location for Fire Suppression Tests}
% 	\label{fig:Room_Nozzle_Location_Fire_Suppression_Tests}
% \end{figure}

@@

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/burnbuilding}
% 	\caption{Delaware County, PA Burn Building}
% 	\label{fig:Delaware_County,_PA_Burn_Building}
% \end{figure}

@@

The interior walls of the burn room were lined with 13~mm (0.5~in) thick cement board. The ceiling of the burn room was the exposed ``floor assembly". The walls of the hallway and entry foyer were composed of 16~mm (0.625~in) Type X gypsum room. The ceiling of the hallway and entry foyer was composed of two layers of 13~mm (0.5~in) thick cement board.

@@

% \subsection{Mass}
% \label{subsec:Mass}

% \subsection{Moisture Content}
% \label{subsec:Moisture_Content}

% \subsection{Infrared Radiation}
% \label{subsec:Infrared_Radiation}

\subsection{Uncertainty}
\label{subsec:Uncertainty}

@@

Wood pallets were used as the fuel source for the gas cooling experiments. The pallets were approximately 1.2~m (4.0~ft) by 1.0~m (3.3~ft) by 0.13~m (0.42~ft) thick. The pallets ranged in mass from 13.6~kg (29.9~lb) to 26.4~kg (58.1~lb) with an average of 18.4~kg (40.5~lbs). The initial fuel load consisted of 10 pallets, arranged in two stacks of five as shown in Fig.~\ref{fig:Pallet_Fuel_Load}. Approximately one half of a bale of excelsior, 13.0~kg (28.6~lb), was mixed with the pallets to aid with ignition. Fig.~\ref{fig:Burn_Building_Fuel_Load}, provides dimensioned locations of the two stacks of pallets within the burn room.

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/PalletFuelLoad}
% 	\caption{Pallet Fuel Load}
% 	\label{fig:Pallet_Fuel_Load}
% \end{figure}

@@

The fuel load for the experiments consisted of one bale of hay, twelve pallets, eleven and a half sheets plywood on the walls and the wood ``floor assembly". Two stacks of pallets with hay were used as the first items ignited in each experiment. Each stack was composed of six pallets with a half bale of hay. The hay was layered between each pallet. Figure~\ref{fig:Wood_Fuel_Load} shows the pallets prior to ignition. The pallets and hay were weighed prior to each experiment. For the four pallet experiments, the average mass of the two stacks of pallets and the bale of hay was 232.4~kg (511.3~lb). A complete listing of the mass of each pallet and hay bales is given in Appendix~\ref{app:fuel_loads}.

@@

>>>>

\headerC{
{
\flushright{
Craig G. Weinschenk \\
Keith M. Stakes \\
Daniel Madrzykowski \\

@@

@@

@@

@@

The interior walls of the burn room were lined with 13~mm (0.5~in) thick cement board. The ceiling of the burn room was the exposed ``floor assembly". The walls of the hallway and entry foyer were composed of 16~mm (0.625~in) Type X gypsum board. The ceiling of the hallway and entry foyer was composed of two layers of 13~mm (0.5~in) thick cement board.

@@

\subsection{Measurement Uncertainty}
\label{subsec:Uncertainty}

@@

Wood pallets were used as the fuel source for the gas cooling experiments. The pallets were approximately 1.2~m (4.0~ft) by 1.0~m (3.3~ft) by 0.13~m (0.42~ft) thick. The pallets ranged in mass from 13.6~kg (29.9~lb) to 26.4~kg (58.1~lb) with an average of 18.4~kg (40.5~lbs). The initial fuel load consisted of 10 pallets, arranged in two stacks of five as shown in Fig.~\ref{fig:Burn_Building_Fuel_Load}. Approximately one half of a bale of excelsior, 13.0~kg (28.6~lb), was mixed with the pallets to aid with ignition. Fig.~\ref{fig:Burn_Building_Fuel_Load}, also provides dimensioned locations of the two stacks of pallets within the burn room.

@@

The fuel load for these experiments consisted of one bale of hay, twelve pallets, eleven and a half sheets plywood on the walls and the wood ``floor assembly". Two stacks of pallets with hay were used as the first items ignited in each experiment. Each stack was composed of six pallets with a half bale of hay. The hay was layered between each pallet. Figure~\ref{fig:Wood_Fuel_Load} shows the pallets prior to ignition. The pallets and hay were weighed prior to each experiment. For the four pallet experiments, the average mass of the two stacks of pallets and the bale of hay was 232.4~kg (511.3~lb). A complete listing of the mass of each pallet and hay bales is given in Appendix~\ref{app:fuel_loads}.

@@

The fuel load for these experiments consisted of 2 sleeper sofas and 2 chairs.
